A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/targeting.tex
change participant number to 14 (it is actually 14)

\subsection{Participants}
We recruited 15 participants from our institution. 13 had never used Glass before. 4 wore prescription glasses, which may have affected their task performance \claire{ as the glasses beneath Glass make it more cumbersome to secure the position of the Glass and to adjust the screen to the optimal angle.}

>>>>

\subsection{Participants}
We recruited 14 participants from our institution. 13 had never used Glass before. 4 wore prescription glasses, which may have affected their task performance \claire{ as the glasses beneath Glass make it more cumbersome to secure the position of the Glass and to adjust the screen to the optimal angle.} Half of them performed {\em infrared} mode first and the other half did {/em list} mode first.
